### 2018-11-21 Sections/physical_architectures_for_quantum_computing.tex
Cross-kerr complete

More recently, as an alternative to using post-selection to simulate strong optical non-linearities, it was shown that by introducing strong coherent states, the strength of  cross-Kerr optical non-linearity can be effectively amplified arbitrarily, allowing even very weak non-linearities to be employed for deterministic entangling gate operations \cite{bib:Munro05}, compensated for by using strong coherent states. Thankfully, strong coherent states are an easy resource to come by nowadays.

In this hybrid linear/non-linear optical architecture, a coherent state is used as a `qubus' (quantum bus)\index{Qubus}, which is entangled with the photonic qubits via the weak non-linear interaction, thereby mediating long-range entangling operations. This can provide the sufficient entangling power needed to enable scalable, universal quantum computation.

Let us describe the operation of a parity measurement\index{Parity measurements} device using weak non-linearities. This gate could subsequently be employed as a fusion gate\index{Fusion!Gates} (Sec.~\ref{sec:fusion_gates}) for building cluster states, and is therefore a resource for universal quantum computation. Simple extensions of the design idea easily generalise to other non-trivial operations, such as CNOT gates or QND measurements\index{Quantum non-demolition measurements}.

The key ingredient here is the cross-Kerr interaction, which obeys the Hamiltonian,
\begin{align}
\hat{H}_\mathrm{ck} = \hbar \chi \hat{n}_a \hat{n}_b,	
\end{align}
where \mbox{$\hat{n}_a = \hat{a}^\dag \hat{a}$} and \mbox{$\hat{n}_b = \hat{b}^\dag \hat{b}$} are the photon-number operators for modes $a$ and $b$ respectively, and $\chi$ is the interaction strength, which is typically very small in the lab. This Hamiltonian generates the unitary transformation,
\begin{align}
\hat{U}_\mathrm{ck} = e^{i\theta\hat{n}_a\hat{n}_b}.
\end{align}
The magnitude of the induced phase-shift is now proportional to,  
\begin{align}
\theta = \chi t,	
\end{align}
where $t$ is the interaction time. For strongly entangling gates we need \mbox{$\theta \approx \pi$}.

@@

\begin{figure*}[!htpb]
	\includegraphics[clip=true, width=\textwidth]{weak_ck_parity_gate}
\caption{Construction of a 2-mode, polarisation-encoded, photonic parity gate using an ancillary qubus coherent state $\ket\alpha$, mediating entangling photonic interactions between $\ket{\psi_a}$ and $\ket{\psi_b}$ via weak cross-Kerr non-linearities (denoted by the controlled-$\theta$ gates). The polarising beamsplitters\index{Polarising beamsplitters} are used to switch between polarisation and dual-rail encoding. The qubus is an optical channel, potentially across long distances for performing distributed gates. The measurement $M$ is a homodyne measurement\index{Homodyne measurements}, which feedforwards to a phase correction.}\label{fig:weak_ck_parity}	
\end{figure*}

Now consider the parity measurement circuit shown in Fig.~\ref{fig:weak_ck_parity}. Let us begin with two polarisation-encoded photonic qubits, which might be separated over long distances,
\begin{align}
\ket{\psi_\mathrm{in}} &= \alpha_{HH} \ket{H}\ket{H} + \alpha_{HV} \ket{H}\ket{V} \nonumber\\
&+\alpha_{VH} \ket{V}\ket{H} + \alpha_{VV} \ket{V}\ket{V}.
\end{align}
Applying the cross-Kerr interactions leaves us in the state,
\begin{align}
\hat{U}_\mathrm{gate} \ket{\psi_\mathrm{in}}\ket\alpha &= [\alpha_{HH} \ket{H}\ket{H}] + \alpha_{VV} \ket{V}\ket{V}]\ket\alpha \nonumber\\
	&+ \alpha_{HV} \ket{H}\ket{V}\ket{\alpha e^{i\theta}}\nonumber\\
	&+ \alpha_{VH} \ket{V}\ket{H}\ket{\alpha e^{-i\theta}}.
\end{align}
Now the qubus state is in some superposition of $\ket\alpha$, $\ket{\alpha e^{i\theta}}$ and $\ket{\alpha e^{-i\theta}}$. The key observation now is that these three coherent basis states become highly distinguishable for large $\alpha$. Specifically, a homodyne measurement on the qubus that projects onto \mbox{$x=0$}, approximately leaves us in the state,
\begin{align}
	\ket{\psi_\mathrm{out}} = \alpha_{HH}\ket{H}\ket{H} + \alpha_{VV}\ket{V}\ket{V},
\end{align}
which corresponds to a maximally-entangling parity or Bell projection\index{Bell!Measurement}.

Clearly, since \mbox{$\braket{\alpha|\alpha e^{\pm i\theta}}\neq 0$}, there is some probability of error. However, we asymptote towards perfect behaviour in the limit of large coherent qubus amplitudes, since,
\begin{align}	
\lim_{|\alpha|\to\infty}\braket{\alpha|\alpha e^{\pm i \theta}} = 0.
\end{align}

This type of distributed gate lends itself very naturally to distributed, network-based implementation, where the quantum internet is employed to mediate the qubus, potentially over long distances.

>>>>

More recently, as an alternative to using post-selection to simulate strong optical non-linearities, it was shown that by introducing strong coherent states, the strength of the non-linear interaction can be effectively amplified arbitrarily, allowing even very weak non-linearities to be employed for deterministic entangling gate operations \cite{bib:Munro05}, compensated for by using strong coherent states. Thankfully, strong coherent states are an easy resource to come by nowadays.

In this hybrid linear/non-linear optical architecture, a coherent state is used as a `qubus' (quantum bus)\index{Qubus}, which is entangled with the photonic qubits via weak non-linear interactions, thereby mediating long-range entangling operations. This can provide the sufficient entangling power needed to enable scalable, universal quantum computation.

Let us describe the operation of a parity measurement\index{Parity measurements} device using weak non-linearities. This gate could subsequently be employed as a fusion gate\index{Fusion!Gates} (Sec.~\ref{sec:fusion_gates}) for building cluster states, and is therefore a resource for universal quantum computation. Simple extensions of this design idea easily generalise to other non-trivial operations, such as CNOT gates or QND measurements\index{Quantum non-demolition measurements}.

The key ingredient here is the cross-Kerr interaction, which obeys the Hamiltonian,
\begin{align}
\hat{H}_\mathrm{ck} = \hbar \chi \hat{n}_a \hat{n}_b,	
\end{align}
where \mbox{$\hat{n}_a = \hat{a}^\dag \hat{a}$} and \mbox{$\hat{n}_b = \hat{b}^\dag \hat{b}$} are the photon-number operators for modes $a$ and $b$ respectively, and $\chi$ is the interaction strength, which is typically very small in the lab. This Hamiltonian generates the unitary transformation,
\begin{align}
\hat{U}_\mathrm{ck} = e^{i\theta\hat{n}_a\hat{n}_b}.
\end{align}
The magnitude of the induced phase-shift is now proportional to photon-number and,  
\begin{align}
\theta = \chi t,	
\end{align}
where $t$ is the interaction time. For strongly entangling gates we need \mbox{$\theta \approx \pi$}.

@@

\begin{figure*}[!htpb]
	\includegraphics[clip=true, width=\textwidth]{weak_ck_parity_gate}
\caption{Construction of a 2-mode, polarisation-encoded, photonic parity gate using an ancillary qubus coherent state $\ket\alpha$, mediating entangling photonic interactions between $\ket{\psi_a}$ and $\ket{\psi_b}$ via weak cross-Kerr non-linearities (denoted by the controlled-$\theta$ gates). The polarising beamsplitters\index{Polarising beamsplitters} are used to switch between polarisation and dual-rail encoding. The qubus is an optical channel, potentially across long distances over the quantum internet for performing distributed gates. The measurement $M$ is a homodyne measurement\index{Homodyne measurements}, which feedforwards to a phase correction. This gate could be used for preparing distributed photonic cluster states, a resource for universal quantum computation.}\label{fig:weak_ck_parity}	
\end{figure*}

Now consider the parity measurement circuit shown in Fig.~\ref{fig:weak_ck_parity}. Let us begin with two polarisation-encoded photonic qubits, which might be separated over long distances,
\begin{align}
\ket{\psi_\mathrm{in}} &= \alpha_{HH} \ket{H}\ket{H} + \alpha_{HV} \ket{H}\ket{V} \nonumber\\
&+\alpha_{VH} \ket{V}\ket{H} + \alpha_{VV} \ket{V}\ket{V}.
\end{align}
Applying the cross-Kerr interactions leaves us in the state,
\begin{align}
\hat{U}_\mathrm{gate} \ket{\psi_\mathrm{in}}\ket\alpha &= [\alpha_{HH} \ket{H}\ket{H}] + \alpha_{VV} \ket{V}\ket{V}]\ket\alpha \nonumber\\
	&+ \alpha_{HV} \ket{H}\ket{V}\ket{\alpha e^{i\theta}}\nonumber\\
	&+ \alpha_{VH} \ket{V}\ket{H}\ket{\alpha e^{-i\theta}}.
\end{align}
Now the qubus state is in some superposition of $\ket\alpha$, $\ket{\alpha e^{i\theta}}$ and $\ket{\alpha e^{-i\theta}}$. The key observation is that these three coherent basis states become highly distinguishable for large $|\alpha|$. Specifically, a homodyne measurement on the qubus that projects onto \mbox{$x=0$}, approximately leaves us in the state,
\begin{align}
	\ket{\psi_\mathrm{out}} = \alpha_{HH}\ket{H}\ket{H} + \alpha_{VV}\ket{V}\ket{V},
\end{align}
which corresponds to a maximally-entangling parity or Bell projection\index{Bell!Measurement}.

Clearly, since \mbox{$\braket{\alpha|\alpha e^{\pm i\theta}}\neq 0$}, there is some probability of error, associated with confusing the coherent basis states and hence their associated photonic qubit states. However, we asymptote towards perfect behaviour in the limit of large coherent qubus amplitudes, since,
\begin{align}	
\lim_{|\alpha|\to\infty}\braket{\alpha|\alpha e^{\pm i \theta}} = 0,
\end{align}
for any \mbox{$\theta\neq 0$}.

This type of non-local gate lends itself very naturally to distributed, network-based implementation, where the quantum internet is employed to mediate the qubus, potentially over long distances.
